Rising from the Ashes: A Metallicity-Dependent Star Formation Gap Splits the Milky Way's $\alpha$-Sequences

### 2025-02-13 paper/ms.tex
Update high-z obs connection

>>>>

\subsection{Connection to High Redshift Quenching}\label{ssec:obshiz}
\edit1{One plausible avenue to producing a \FeH{}-dependent halt in star formation is through a global quiescent period. Galaxies which undergo a starburst to quiescence to rejuvenation sequence (post-starburst galaxies, or PSBs) are observed at high-$z$ ($z>1$), and may be plausible Milky Way-progenitors.} With abundance matching, we expect the Milky Way's total stellar mass to be $\sim10^{10.3}\,\Msun$ at $z\sim2$ \citep{2013ApJ...771L..35V}. A number of authors have explored PSBs and quiescent galaxies at slightly higher masses at $z\sim2$, with large advances in the post-JWST era.

Furthermore, \citet{2023arXiv231215012C} found that lower mass quiescent galaxies (towards $10^{10.3}\,\Msun$) tend to be younger and more disky, pointing to a merger driven scenario. There is also evidence that AGN, which we \edit1{suspect might} be responsible for the \edit1{star formation gaps} in our system (Appendix~\ref{app:cause_qui}), is operating at these redshifts \citep[e.g.][and references therein]{2023arXiv230806317D,2024arXiv240417945P,2024arXiv240518685M,2024Natur.630...54B}.

\edit1{In the context of our proposed mechanism, only a metallicity-specific quenching period is necessary for generating an $\alpha$-bimodality. This may correspond to inside-out or outside-in quenching, for which examples are known in the local and high-$z$ universe \citep[e.g.,][]{2015Sci...348..314T,2019ApJ...872...50L}.}
